Here is a guide to using caret package in predictive modelling: https://www.r-project.org/conferences/useR-2013/Tutorials/kuhn/user_caret_2up.pdf

It is a useful package that consists of functions that unify predictive models from different packages.
It contains functions to do basic stuff like train test split in R.

Setup
```{r setup}
library(kernlab)
library(caret)
```
Creat data split
```{r}
?createDataPartition #shows up other useful functions as well
data("spam")
train <- createDataPartition(y = spam$type, p = 0.75, list = FALSE)
training <- spam[train,]
testing <- spam[-train,]
```
This function creates a training model and the performance measured is calculated based on resampling measure bootstrap
```{r}
model <- train(type ~ ., data = training, method = "glm")
model$finalModel # to view the final model
prediction <- predict(model,newdata= testing)
prediction
confusionMatrix(prediction,testing$type)
```
The train function comes with other bunch of arguments that might prove to be useful, for example it has metric argument to evalute the model performance, They are
1. For continous y
      - RMSE (default)
      - R-squared
2. For indicator y
      - Accuracy
      - Kappa
To further control the parameters of the train function, we can use trainControl function
```{r}
?trainControl
args(trainControl)
```
featurePlot in caret package to create a plot of the features
```{r}

```

