---
title: "colors"
author: "Gaurav"
date: "8/11/2019"
output: html_document
---

```{r setup}
library(grDevices)
library(RColorBrewer)
```

The gray function interpolates b/w black(0) and white(1) 
```{r gray}
gray(1)
gray(0.5)
```
colorRamp and colorRampPalette
```{r}
?colorRamp #returns function that takes value b/w 0 and 1 to return a color from the palette
?colorRampPalette #returns function that takes integer argument for no of colors from the palette
```

```{r}
pal <- colorRamp(c("red","blue"))
pal(0)
pal(1)
pal(0.5)
```
```{r}
pal <- colorRampPalette(c("red","yellow"))
pal(1)
pal(2)
pal(10)
```
There are 3 types of palettes available from the RColorBrewer package:
- Sequential: For ordered data, like cont data
- Diverging: When representing diverging behaviour from something, for example data going in two different directions such as correlation, negative and postive
- Qualitative: Not ordered, like factors
```{r}
cols <- brewer.pal(3,"BuGn") # the name needs to be looked from the help page
pal <- colorRampPalette(cols)
image(volcano,col=pal(20))
```
```{r}
x <- rnorm(10000)
y <- rnorm(10000)
smoothScatter(x,y) #dark blue region is where most points are, high-density region
```

