###Date and Time

In R, date is and time belong to classes Date and POSIXct/POSIXlt respectively. Date is internally stored as in integer representing the number of days from 1-1-1970. POSIX probably stands for Portable Operating System Interface (POSIX) which are standards to ensure compatability b/w different OS. 'ct' stands for calendar time and 'lt' stands for local time. POSIXct stores the time as number of seconds since 1-1-1970 and POSIXlt stores it as a list of hour, min, sec, tzone (timezone) etc.
```{r basic}
Sys.Date() #To get current date, similarly for time Sys.time()
unclass(Sys.Date()) #It'll be an integer, number of days since 1-1-1970
```
Checking internal representation
```{r}
t1 <- Sys.time() #default class is POSIXct, POSIXt is the parent class apparently
t2 <- as.POSIXlt(Sys.time())
unclass(t1) #how POSIXct is stored
str(unclass(t2)) # how POSIXlt is stored
```
```{r}
#functions such as 
months(t2)
weekdays(Sys.Date())
quarters(t1)
#can be used to get more information out of date and time objects
```
```{r}
#Use strptime read as string parse time to parse string as time object
?strptime
```
Arithmatic operations can also be performed on date and time objects
```{r}
t1 > t2
difftime(t1,t2, units = 'mins')
```

