
# Starting with regularization

1st if you have more predictors than samples than you may get non zero value for some predictors
but Na for the others. Regularziation allows for preudctors to have zero coefficients, the predictors which are not as informative. 

Ridge regression:
$\lambda $ term with $ \beta^2 $, ie, $\lambda \beta^2$, this is similar to keeping the sum of
$\beta^2$ less than some constant s inversely proportional to $\lambda$. So $\lambda$ is a penalty and a value of zero would mean the same as least squares and at value of infinity all
coeeficients would equal to zero.

Lasso regression:
Similar to ridge but the penalty term is $\lambda |\beta|$, it has a closed form solution, it basically reduced all the parameters by a gamma value and those with an absolute value less than gamma are set to zero. 

There are lecture notes by Hector Corrado Bravo on practical machine learning

method = ridge, lasso and relaxo in caret

# Combining Classifiers

We can also develop ensemble models that use multiple machine learning models to make prediction. If we have say 5 independet classifiers with 0.7 accuracy each than the majority
vote accuracy will be 10*0.7^3*0.3^2 + 5*0.7^4*0.3 + 0.7^5. The accuracy calculation is already present in the classifiers. What percentage of data does all classifiers classify in agreement, 0.7^5. 

Using bagging, boosting and random forest are methods of combining models. The others are:
- Model stacking and
- Model Ensembling

Fitting a model that combines predictors

```{r setup}
library(caret)
library(randomForest)
library(ISLR)
library(dplyr)
library(ggplot2)
```

```{r}
data(Wage)
set.seed(123)
wage <-  Wage %>% select(-logwage)
inBuild <- createDataPartition(y=wage$wage,p=0.7,list=F)
validation <- wage[-inBuild,]
buildData <- wage[inBuild,]
inTrain <- createDataPartition(y=buildData$wage,p=0.7,list=F)
training <- buildData[inTrain,]
testing <- buildData[-inTrain,]
```

Build two models on the dataset
```{r}
mod1 <- train(wage ~ ., data = training, method = 'glm')
mod2 <- train(wage ~ ., data = training, method = 'rf', trControl = trainControl(method = 'cv'),number = 3 )
```

```{r}
pred1 <- predict(mod1,testing)
pred2 <- predict(mod2,testing)
qplot(pred1,pred2,color=wage,data=testing)
```


```{r}
predDf <- data.frame(pred1,pred2,wage=testing$wage)
modCombine <- train(wage ~ ., data = predDf, method = 'gam')
```

```{r}
# prediction for combined model on validation set 
predV1 <- predict(mod1,validation)
predV2 <- predict(mod2,validation)
predVDf <- data.frame(predV1,predV2,wage=validation$wage)
sqrt(sum((validation$wage - predict(mod1,validation))^2))
sqrt(sum((validation$wage - predict(mod2,validation))^2))
sqrt(sum((validation$wage - predict(modCombine,predVDf))^2))
```

typical model for classification involves building odd number of models and then assigning based on majority after prediction from each model


## Quiz

```{r}
library(ElemStatLearn)

data(vowel.train)

data(vowel.test)
```

```{r}
vowel.train$y <- as.factor(vowel.train$y)
vowel.test$y <- as.factor(vowel.test$y)
set.seed(33833)
modRf <- train(y ~ . , data = vowel.train, method = 'rf')
modGbm <- train(y ~., data = vowel.train, method = 'gbm', verbose = F)
```

```{r}
predRf <- predict(modRf, vowel.test)
predGbm <- predict(modGbm, vowel.test)
sum(predRf == vowel.test$y)/nrow(vowel.test)
sum(predGbm == vowel.test$y)/nrow(vowel.test)
agree <- which(predRf == predGbm)
sum(predRf[agree] == vowel.test$y[agree])/length(agree)
```

Q2 
```{r}
library(caret)

library(gbm)

set.seed(3433)

library(AppliedPredictiveModeling)

data(AlzheimerDisease)

adData = data.frame(diagnosis,predictors)

inTrain = createDataPartition(adData$diagnosis, p = 3/4)[[1]]

training = adData[ inTrain,]

testing = adData[-inTrain,]
```
```{r}
set.seed(62433)
modRf <- train(diagnosis ~ ., data = training, method = 'rf')
modGbm <- train(diagnosis ~ ., data = training, method = 'gbm', verbose = F)
modLda <- train(diagnosis ~ ., data = training, method = 'lda')
```
```{r}
p1 <- predict(modRf,testing)
p2 <- predict(modGbm, testing)
p3 <- predict(modLda, testing)
predDf <- data.frame(p1,p2,p3,diagnosis= testing$diagnosis)
modAll <- train(diagnosis ~ ., data = predDf, method = 'rf')
```
```{r}
sum(p1==testing$diagnosis)/length(p1)
sum(p2==testing$diagnosis)/length(p2)
sum(p3==testing$diagnosis)/length(p3)
sum(predict(modAll,testing)==testing$diagnosis)/nrow(testing)
```
```{r}
set.seed(3523)

library(AppliedPredictiveModeling)

data(concrete)

inTrain = createDataPartition(concrete$CompressiveStrength, p = 3/4)[[1]]

training = concrete[ inTrain,]

testing = concrete[-inTrain,]
```

```{r}
library(elasticnet)
set.seed(233)
mod <- enet(as.matrix(training[,-9]),training$CompressiveStrength,0)
plot.enet(mod)
```


## 4 forcasting

```{r}
library(lubridate) # For year() function below

dat = read.csv("gaData.csv")

training = dat[year(dat$date) < 2012,]

testing = dat[(year(dat$date)) > 2011,]

tstrain = ts(training$visitsTumblr)
```

```{r}
library(forecast)
```

```{r}
mod <- bats(tstrain)
pred <- forecast(mod, h = 600)
sum((testing$visitsTumblr < pred$upper[366:600,2]) & (testing$visitsTumblr > pred$lower[366:600,2]))/nrow(testing)
```


## 5

```{r}
set.seed(3523)

library(AppliedPredictiveModeling)

data(concrete)

inTrain = createDataPartition(concrete$CompressiveStrength, p = 3/4)[[1]]

training = concrete[ inTrain,]

testing = concrete[-inTrain,]
```

```{r}
library(e1071)
set.seed(325)
modSvm <- svm(CompressiveStrength ~ . , data = training)
pred <- predict(modSvm,testing)
sqrt(sum((pred - testing$CompressiveStrength)^2))
```

