---
output:
  pdf_document: default
  html_document: default
---
## Lattice plotting system

Lattice package for plotting is very efficient in visualizing data as large number of plots with few lines of
code.
```{r setup}
library(lattice)
library(datasets)
```
There is a difference in the plots if called with factor in lattice command. The first one which
contains the argument as.factor(Month) plots the data with months as title for individual plots
but without being a factor it misses the individual title.
```{r}
xyplot(Ozone ~ Wind | as.factor(Month), data = airquality, layout = c(5,1))
xyplot(Ozone ~ Wind | Month, data = airquality, layout = c(5,1))
```
It can be used even for generating plots for 2 conditions, price ~ carat conditioned on color and cut
```{r}
library(ggplot2)
xyplot(price~carat | color*cut, data = diamonds, pch = 20, xlab = "Carat", ylab = "Price", main = "Price vs carat conditioned on color and cut")
#argument strip = FALSE will remove the condition labels
```
Mosaic plot: For plotting contingency tables
```{r}
dat <- data.frame(
  "smoke_no" = c(7, 0),
  "smoke_yes" = c(2, 5),
  row.names = c("Athlete", "Non-athlete"),
  stringsAsFactors = FALSE
)
colnames(dat) <- c("Non-smoker", "Smoker")
mosaicplot(dat,
  main = "Mosaic plot",
  color = TRUE
)
```

